% \lhead{Ayi Giri Nandini}
% \rhead{Sanskrit 2}

\chordsoff

\beginsong{Ayi Giri Nandini}[]

    \beginverse
        Ayi Giri Nandini Nandit. Medini
        Vishw. Vinodini Nandinute
        Girivar. Vindhya Shirodhini Vasini 
        Vishnu Vilasini Vishnu Nute 
        Bhagavati He Shiti Kanth. Kutumbini 
        Bhu ri Kutumbini Bhu ri krute
    \endverse
    
    \beginchorus
        {\bf Chorus}: 
        Jay. Jay. Hai Mahishasur. Mardini \} 
        Ramyak. Par.dini Shailasute \} x3 
    \endchorus
    
    \beginverse
        Sur.var. Varshini Dur.dhar. Dhar.shini 
        Dur.mukh. Marshini Har.sharate  
        Tribhuvan. Poshini Shankar. Toshini 
        Kilmisha Moshini Ghosharate 
        Danuj. Niroshini Kshit. sut.roshini 
        Dur.mud. Shoshini Sindhusute 
    \endverse
    
    \beginverse
        Ayi Shat. Khanda Vikhandit. Runda 
        Vitundit. Shunda Gajadhipate 
        Ripugaja Ganda Vidarana Chanda 
        Parakrama Shunda Mrugadhipate 
        Nijabhuj. Danda Nipatit. Chanda 
        Vibhatit. Munda mathadhipate 
    \endverse
    
    \beginverse
        Dhanu Ranu Sanga Rana Kshana Sanga 
        Parisphut. Danga Natatkatake 
        Kanak. Pishanga Pushatka Nishanga 
        Rasad Bhata Shrunga Hata Batuke 
        Krut. Chaturanga Bala Kshiti Ranga 
        Ghatad. Bahu RangaRatad. Batuke 
    \endverse
    
    \beginverse
        Jay. Jay. Japya Jaye Jay. shabda 
        Parastuti Tatpara Vishwanute 
        Jhana Jhana Jhinjhita Jhinkruta Nupura 
        Jhinjita Mohita Bhutapate 
        Natina Natartha Natin. Nata Nayaka 
        Natita Nataya Yuganu Rate 
    \endverse
    
    \beginverse
        Ayi Sumanas Sumanas Sumanas 
        Sumanas Sumanohara Kantisute 
        Shrit. Rajani Rajani Rajani 
        Rajani Rajani kara Vakravrute 
        Sunayana Vibhrama Rabhrama Rabhrama 
        Rabhrama Rabhrama Radhipate 
    \endverse
    
    \beginverse
        Sahita Maharnava Malla Mattalika 
        Vallika Rallika Mallarate 
        Vir.chita Vallika Pallika Mallika 
        Jhillika Bhillika Vargavrute 
        Sitakruta Phulli Samulla Sitaruna 
        Tallaja Pallava Sallalite 
    \endverse
    
    \beginverse
        Kamala Dalamala Komala Kanti 
        Kala Kalikamala Bhala Late 
        Sakala Vilasa Kala Nilayakrama 
        Keli Chalatkala Hansa Kule 
        Alikula Sankula Kuvalaya Mandala 
        Mauli Milad Bakulati Kule 
    \endverse

\endsong

% Insert new page after complete bhajan.
\newpage